---
title: "Set up MTurk survey"
output: html_notebook
---

# Connect to MTurk API

```{r}
devtools::install_github("cloudyr/pyMTurkR#18") #Qualification requirement for HITTypes do not work in CRAN version 1.1.4 - fixed in this PR

library(pyMTurkR)
source("parameters.R") #Includes setting of access keys
options(pyMTurkR.sandbox = F)

#Check connection
#AccountBalance()
```


# Create qualifications and qualification requirement

## Set parameters

```{r}
project_name <- "Covid" #used as prefix for qualification
min_HITs <- 100 #Minimum number of completed HITs required. Suggested: at least 100
min_approved <- 90 #Minimum share of HITs approved (%). Suggested: at least 90
locations <- list(Country = "US")

blacklist <- "3Z51ZTGR644Q1WDP87483T7ZE95WZY" #QualificationTypeId of blacklist to be used, if any

```

## Create duplication qual and save its ID

Run as is and save compl_qual_id to parameters.R

```{r}
# create QualificationType to prevent duplicate responses
compl_qual <- CreateQualificationType(name=paste0(project_name, ": Already completed HIT"),
                                description="Already completed identical HIT before.",
                                status = "Active")

compl_qual_id <- compl_qual$QualificationTypeId

```


## Set up standard qualification

Run as is.

```{r}
# Set up standard qualifications
quals <- list(
  list( #Number of HITs
    QualificationTypeId = "00000000000000000040", Comparator = "GreaterThan", IntegerValues = min_HITs, RequiredToPreview = TRUE
  ), list( #Country
    QualificationTypeId = "00000000000000000071", Comparator = "EqualTo", LocaleValues = locations, RequiredToPreview = TRUE 
  ), list( #Percent Approved
    QualificationTypeId = "000000000000000000L0", Comparator = "GreaterThan", IntegerValues = min_approved, RequiredToPreview = TRUE
  ))

# Add extra qualification - duplicate marker and individual blacklist

quals <- c(quals, 
    list(list(  #Extra qualification - not yet participated
    QualificationTypeId = compl_qual_id, Comparator = "DoesNotExist", RequiredToPreview = TRUE
  )))

if (!is.null(blacklist)) {
  quals <- c(quals, list(list(
  QualificationTypeId = blacklist, Comparator = "DoesNotExist", RequiredToPreview = TRUE
)))
}


qreq <- GenerateQualificationRequirement(quals)



```

# Create HITType and question

## Set parameters

```{r}

HIT_attributes <- list(
  title="Survey on life during the coronavirus pandemic",
  #Short description shown before workers click on HIT
  description= "Complete a 10-12-minute academic research survey about your life during the coronavirus pandemic",
  #Reward per HIT in USD
  reward="1.25",
  #Duration = time until timeout, should be much longer than survey
  duration=seconds(hours=1), 
  #Time until auto-approval - cannot reject after that anymore
  auto.approval.delay = seconds(days=4),
  keywords="survey, questionnaire, research")

question_attributes <- data.frame(
  # Title and description of HIT - shown after worker clicked on it
  Title = "Survey on life during the coronavirus pandemic", 
  Description = "We are running an academic research project the effects of Covid-19 on everyday life. For that, we invite you to answer a 10-12 minute academic research survey about how the pandemic affects you and how you are doing at the moment",
  # Javascript code to validate survey code entered - "true" to skip
  Code_validation = "x >= 100000 && x <= 999999",
  #Survey link - cannot contain URL parameters! (i.e. no ? in link)
  Link = "https://goldpsych.eu.qualtrics.com/jfe/form/SV_5pdxFrbtFfL6YPb"
)


```


## Create HIT and question HTML file

Run as is and save HITType_id to parameters.R

```{r}
#Register type
HIT_attributes <- c(HIT_attributes, qual.req = list(quals))
HITType <- do.call(RegisterHITType, HIT_attributes)
HITType_id <- HITType$HITTypeId

hits <- GenerateHITsFromTemplate(template = "survey_template.html", input = question_attributes)

writeLines(hits[[1]], "survey_details.html")

```

# Optional: receive email when new HIT is reviewable

Particularly helpful when survey_run.R is run on a VM or in some other place where it is not easily monitored.

```{r}
a <- GenerateNotification("lukas.wallrich@gmail.com", "Email", "HITReviewable")

SetHITTypeNotification(hit.type = HITType_id,
notification = a,
active = TRUE)

# send test notification
SendTestEventNotification(a, test.event.type = "HITReviewable")

```

